|

### 2020-06-02 nontex/install/git/fs_git_setup.Rmd
8 pane file complete

gem install jekyll bundler
jekyll -v
gem install bundler
gem install minima
gem install jekyll-feed

cd ~/fanwangecon.github.io
<!-- delete existing Gemfile Gemfile.lock possibly in directory -->
bundle init
bundle config set --local path 'vendor/bundle'
bundle add jekyll
bundle add minima
bundle add jekyll-feed
bundle exec jekyll new --force --skip-bundle .

>>>>

gem install jekyll bundler
jekyll -v
gem install bundler
gem install minima
gem install jekyll-feed
gem install jekyll-sitemap

cd ~/fanwangecon.github.io
<!-- delete existing Gemfile Gemfile.lock possibly in directory -->
bundle init
bundle config set --local path 'vendor/bundle'
bundle add jekyll
bundle add minima
bundle add jekyll-sitemap

### 2020-06-02 nontex/install/windows/fn_installations.Rmd
8 pane file complete

```{bash}
ipython
import pyfan.util.rmd.bookdownparse as bookdownparse
?bookdownparse.fs_yml2readme
```
##### Uninstall

@@

@@

```{bash}
# Set up
conda list env
conda env remove -n wk_perl
conda create -n wk_perl -y
conda activate wk_perl
conda install -c anaconda perl
conda list
conda deactivate

# intall packages in virtual env
cd "C:\Users\fan\.conda\envs\wk_perl\"
git clone https://gitlab.com/latexpand/latexpand.git

@@

```{r}
# Set up
conda deactivate
conda list env
conda env remove -n wk_nodejs
conda create -n wk_nodejs -y
conda activate wk_nodejs

conda install -c conda-forge nodejs -y
# ended up downloading installer for windows nodejs and installing out of conda
# was having lots of bugs
npm i -g --production windows-build-tools
npm install -g --force decktape
# use yaml2tex

cd "C:\Users\fan\Documents\Dropbox (UH-ECON)\repos\fanwangecon.github.io\_cv\templating\"
python yaml2tex.py
```

## Essential Programs to Install

@@

# Install Tools to Work with Other Packages
install.packages(c("reticulate"))

@@

- see all shortcuts: *Ctrl + k, ctrl + s*
- Zen model: *Ctrl + k, z*, this means press control k, then press z
    + note that z mode can be adjusted by shiftin the bar on the left
- Open up Settings: *Ctrl + ,*
- Preview Markdown in VSCode: *Ctrl + Shift + v*
- Open up left pane: *Ctrl + b*
- Wrap Text: *alt + z*, switch between wrap or not to save screen space for example.
- Hide Console Pane (running code): *Ctrl + j*

@@

>>>>

```{bash}
ipython
import pyfan.util.rmd.bookdownparse as bookdownparse
?bookdownparse.fs_yml2readme
```

##### Uninstall

@@

##### pyfan workflow and files added

New python functions are added, or new Rmd files are added with python exampls.

List of to dos and checks.

New rmd files:

1. Edit yaml to include functions used
  + Go over each part, add to short desc
  + In each section, add code usage
2. Link to py functions if implemented there
3. Run file internally
4. Add new files to *_bookdown.yml*
5. Run pyfan rmd compile
6. Overall bookdown check pdf and html

New py functions:

1. Document with function name, parameters and returns
2. update version number
3. Test run the function file's main 
4. Local sphnix text etc
5. Poetry publish
6. Git push 
7. Check Docs on readthedocs
8. Uninstall and install locally
9. Uninstall and install in wk_pyfan envir

```{bash}
cd "C:/Users/fan/pyfan"
poetry install

rm -rf dist/ build/ docs/
mkdir docs
cd docs/
sphinx-build -b html ../ _build

```{bash}
pip show pyfan
<!-- pip install pyfan -->
pip uninstall pyfan -y
pip install pyfan
pip install git+https://github.com/fanwangecon/pyfan.git#egg=pyfan

conda activate wk_pyfan
pip uninstall pyfan -y
pip install pyfan
pip install git+https://github.com/fanwangecon/pyfan.git#egg=pyfan
conda deactivate
```

@@

```{bash}
# Set up
conda deactivate
conda list env
conda env remove -n wk_perl
conda create -n wk_perl -y
conda activate wk_perl
conda install -c anaconda perl -y
conda list
conda deactivate

# intall packages in virtual env
cd "C:\Users\fan\.conda\envs\wk_perl\"
cd "C:\ProgramData\Anaconda3\envs\wk_perl\"
git clone https://gitlab.com/latexpand/latexpand.git

@@

```{r}
# Set up
conda deactivate
conda list env
conda env remove -n wk_pyfan
conda create -n wk_pyfan -y
conda activate wk_pyfan

# add channel
conda config --env --add channels conda-forge
conda config --get channels
conda config --get channels --env

# yaml
conda install python-frontmatter -y
conda install pyyaml -y

# environment data
conda install cdsapi -y
conda install -c conda-forge eccodes -y

# pyfan install 
pip install pyfan

#### Conda Bookdown for pyfan

```{bash}
# Set up
conda deactivate
conda list env
conda env remove -n wk_perl
conda create -n wk_perl -y
conda activate wk_perl
conda install -c anaconda perl -y
conda list
conda deactivate

# intall packages in virtual env
cd "C:\Users\fan\.conda\envs\wk_perl\"
cd "C:\ProgramData\Anaconda3\envs\wk_perl\"
git clone https://gitlab.com/latexpand/latexpand.git

# use latexpand
conda activate wk_perl
cd "C:\Users\fan\Documents\Dropbox (UH-ECON)\Project Emily Minority Survey\Drafts_RR\OverleafChinaSchoolClosure"
perl "C:\Users\fan\.conda\envs\wk_perl\latexpand\latexpand" draft_edcc_submit_rr.tex > draft_edcc_submit_rr_flat.tex
```
## Essential Programs to Install

@@

# Install Tools to Work with Other Packages
install.packages(c("reticulate", "JuliaCall"))

@@

- see all shortcuts: *Ctrl + k, ctrl + s*
- Zen model: *Ctrl + k, z*, this means press control k, then press z
    + note that z mode can be adjusted by shiftin the bar on the left
- Open up Settings: *Ctrl + ,*
- Open up Extensions: *Ctrl + Shift + X*
- Preview Markdown in VSCode: *Ctrl + Shift + v*
- Open up left pane: *Ctrl + b*
- Wrap Text: *alt + z*, switch between wrap or not to save screen space for example.
- Hide Console Pane (running code): *Ctrl + j*

@@

### VSCode Spell Check

Download [Spell Right](https://marketplace.visualstudio.com/items?itemName=ban.spellright).
